A Case Study in Preserving a High Energy Physics Application

### 2014-01-18 paper.tex
Add process of .svg into Makefile &two pics

@@

\section{Solution 3 to Repeat the Program}
\subsection{Working principle of Packaging Utility}
The difficulty of data access authority acquisition enforces us to find out one solution, in which the reproduction of the original analysis can be done without any external dependency. That is, one independent and self-contained package containing all the data and software dependencies is necessary. Someone may suggest that it should be the responsibility of the original author to generate the required package. However, letting the original author to provide the package which can be used by others to repeat the original experiment is unrealistic. One reason is that figuring out the underlying dependency of each software is complex and time-consumpting and even impossible for the original author. In this experiment, the machine used for the experiment is one public machine of physics department, and Matthias is one common user without root authority. The underlying OS and supporting softwares are installed and maintained by the IT department of the university. On the other hand, the architecture design of the required package including all the data and software dependencies is not under the research field of physists.

@@

@@

>>>>

\begin{figure*}
\centering
\epsfig{file=overview-of-architecture.eps, height=6in, width=7in}
\caption{Overview of Architecture}
\label{fig:Overview of architecture}
\end{figure*}

@@

\section{Solution 3 to Repeat the Program}
The overview of the architecture is shown in ~\ref{fig:Overview of architecture}.

\subsection{Working principle of Packaging Utility}
The difficulty of data access authority acquisition enforces us to find out one solution, in which the reproduction of the original analysis can be done without any external dependency. That is, one independent and self-contained package containing all the data and software dependencies is necessary. Someone may suggest that it should be the responsibility of the original author to generate the required package. However, letting the original author to provide the package which can be used by others to repeat the original experiment is unrealistic. One reason is that figuring out the underlying dependency of each software is complex and time-consumpting and even impossible for the original author. In this experiment, the machine used for the experiment is one public machine of physics department, and Matthias is one common user without root authority. The underlying OS and supporting softwares are installed and maintained by the IT department of the university. On the other hand, the architecture design of the required package including all the data and software dependencies is not under the research field of physists.

@@

\begin{figure*}
\centering
\epsfig{file=preservation-integration.eps, height=4in, width=6in}
\caption{Preservation Integration of Multiple Programs}
\label{fig:Preservation integration}
\end{figure*}

@@

The architecture of preservation integration of multiple programs is shown in ~\ref{fig:Preservation intergration}.
